---
title: "httr扩展包测试学习报告"
author: "hulilei"
date: "2018/10/28"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
   library(httr);
```

## httr主要设计目标

  The aim of httr is to provide a wrapper for the curl package, customised to the demands of modern web APIs.
  
## httr主要功能特色

1. Functions for the most important http verbs: **GET(), HEAD(), PATCH(), PUT(), DELETE() and POST()**.包含http协议的主要函数
1. Automatic connection sharing across requests to the same website (by default, curl handles are managed automatically), cookies are maintained across requests, and a up-to-date root-level SSL certificate store is used.自动管理cookies与SSL状态信息
1. Requests return a standard reponse object that captures the http status line, headers and body, along with other useful information.返回标准的响应对象，包含状态,数据包头,数据包体及其他有用信息。
1. Response content is available with content() as a raw vector (as = "raw"), a character vector (as = "text"), or parsed into an R object (as = "parsed"), currently for html, xml, json, png and jpeg.提供3种输出格式,包含原始数据，文本及R对象
1. You can convert http errors into R errors with **stop_for_status()**.获取http的错误信息
1. Config functions make it easier to modify the request in common ways: set_cookies(), add_headers(), authenticate(), use_proxy(), verbose(), timeout(), content_type(), accept(), progress().提供修改访问请求的函数，方便修改相关的请求信息
1. Support for OAuth 1.0 and 2.0 with oauth1.0_token() and oauth2.0_token(). The demo directory has eight OAuth demos: four for 1.0 (twitter, vimeo, withings and yahoo) and four for 2.0 (facebook, github, google, linkedin). OAuth credentials are automatically cached within a project.支持OAuth1.0与2.0的支持

## httr的安装

### 从CRAN中的安装

`install.packages("httr")`

### 从GitHub上安装
`devtools::install_github("r-lib/httr")`



## 快速上手,出发！！

### GET应用
```{r}
    r <- GET("http://httpbin.org/get")

     r;
```

其中R是`r class(r)`类的`r typeof(r) `,一共有`r length(r)`个元素，元素名称分别为`r names(r)`。

### status_code()获取状态代码
```{r}
     status_code(r);
```

### http_status()获取状态信息，不仅仅是代码
```{r}
    http_status(r);
    r$status_code;
```


### headers()获取头部信息
```{r}
   headers(r);
```

### content()获取内容
```{r}
   content(r);
   str(content(r));
```

### GET  with query
```{r}
  baidu12306 <-GET('https://www.baidu.com/s',query=list(wd=12306));
  content(baidu12306,'text');
  cookies(baidu12306);
```

### cookies()获取相应的信息

```{r}
   r1 <- GET("http://httpbin.org/cookies/set", query = list(a = 1))
    cookies(r1)
    r <- GET("http://httpbin.org/cookies/set", query = list(b = 1))
    cookies(r)
```


## request 请求的处理

### GET

```{r}
r <- GET("http://httpbin.org/get", 
  query = list(key1 = "value1", key2 = "value2")
)
content(r)$args

```
如果相应的参数被应用为NULL，则系统将自动删除此元素
```{r}
r <- GET("http://httpbin.org/get", 
  query = list(key1 = "value 1", "key 2" = "value2", key3 = NULL))
content(r)$args
```

### POST()
```{r}
  # r <- POST("http://httpbin.org/post", body = list(a = 1, b = 2, c = 3))

url <- "http://httpbin.org/post"
body <- list(a = 1, b = 2, c = 3)
# Form encoded
r_form <- POST(url, body = body, encode = "form");
r_form;
# Multipart encoded
r_multipart <- POST(url, body = body, encode = "multipart");
r_multipart;
# JSON encoded
r_json <- POST(url, body = body, encode = "json");
r_json;
```

### POST WITH FILES
```{r}
r_file <- POST(url, body = upload_file("mypath.txt"));
r_file;
```

